---
title: "Graphic_description"
categories:
  - Data Sciences I 
description: This article is about a study on the sea urchin. This article compares those of the farm and those of the sea. 


author:
  - name: Lise VE
    url: {}
date: 11-10-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#package
SciViews::R
```

```{r importation}
data <- read("urchin_bio", package = "data.io")
```

### Introduction

I decide to look the maturity between the sea urchin which come from sea or farm.So I take data for to compare with a graphic which show the potential difference.   

```{r}
chart(data = urchin_bio, ~ maturity %fill=% origin) +
  geom_bar(position = "dodge") +
  ylab("Effectifs") +
  scale_fill_viridis_d()

```


After analysis of these graphics we can see that the sea urchin from farm are less likely to reach maturity than those of sea. Those of the farm are greater number to be immature(More 150 individuals against less 150 indviduals for those of sea). Concerning the maturity between 1-2 years those of sea are more present.Of general way, the majority of specie no matter their origin, they don't have maturity.  

